---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(janitor)
```
```{r}
code_clan_info <-read_csv("data/code_clan_info.csv")
code_clan_tweets <-read_csv ("data/code_clan_tweets.csv")
```

Q1 Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
code_clan_tweets%>%
head()

```
```{r}
code_clan_tweets%>%
nrow()
```


Q2 Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. 

checking Variables Names
```{r}
names (code_clan_tweets)
```
```{r}
glimpse (code_clan_tweets)
```

```{r}
view(code_clan_tweets)
```
#This them gave me the glimpse - worked well

```{r}
str(code_clan_tweets)
```




#THis is where is got stuck - checked the answers
```{r}
code_clan_tweets%>%
  filter(is_quote)

```

view (code_clan_tweets
dim
names
head

```{r}
code_clan_tweets %>%
  filter(is_quote == FALSE) %>%
  summarise(total = sum(favorite_count))
```
Q3 Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.
summarise
split by the type = group by
summarise at the end and logical order of the oprations.

```{r}

  mean_retweets <- code_clan_tweets %>%
  filter(is_quote == FALSE) %>%
  group_by(source) %>%
  summarise(average_retweet = mean(retweet_count))
  head(mean_retweets)
```


Q4
#Count the total number of likes (i.e. total of favorite_count),
#split by media type,
#and arrange them from most likes to least. 
#Assume that any tweets without a listed media type are of type “text”.

```{r}
code_clan_tweets %>%
  mutate(media_type = coalesce(media_type, "text")) %>%
  group_by(media_type) %>%
  summarise(favourite_count_total = sum(favorite_count)) %>%
  arrange(desc(favourite_count_total))
```

#Q5

Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).

```{r}
code_clan_tweets %>%
  summarise(avg_tweet_length = mean(display_text_width))
```

```{r}
code_clan_tweets
```

```{r}
code_clan_tweets %>%
  mutate(char_count)
```

Q6The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.





```{r}
code_clan_tweets%>%
  count(tweet_id)
```

```{r}
info <- read_csv("data/code_clan_info.csv")
  
  joined_tweets <- code_clan_tweets %>%
    full_join(info,
              by = "tweet_id")
```

```{r}
code_clan_info
```

```{r}
user_pattern <- "@[a-zA-Z0-9_]+"
tweets <- codeclan_tweets %>% 
  select(text)
head(str_extract_all(tweets$text, user_pattern))
```
```{r}
code_clan_tweets%>%
  str_count("(?i)Codeclan")
```
```{r}

code_clan_tweets %>%
  pattern <- "CodeClan"
  code_clan_tweets
  str_count()
```

```{r}
code_clan_tweets %>%
  str_count("(?i)Edinburgh")
```



#Extension Question 10


```{r}
user_pattern <- "@[a-zA-Z0-9_]+"
tweets <- code_clan_tweets %>% 
  select(text)
head(str_extract_all(tweets$text, user_pattern))
```

```{r}
code_clan_tweets %>%
  select(text) %>%
  mutate(user_tweeeted = str_extract_all(text, "@[A-z0-9_]+")) %>%
  unnest(cols = c(user_tweeeted)) %>%
  group_by(user_tweeeted) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

