---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(janitor)
```
```{r}
code_clan_info <-read_csv("data/code_clan_info.csv")
code_clan_tweets <-read_csv ("data/code_clan_tweets.csv")
```

Q1 Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
code_clan_tweets
head()

```
```{r}

col(code_clan_tweets)
```

```{r}
nrows()
```


Q2 Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. 

checking Variables Names
```{r}
names(code_clan_tweets)
```
```{r}
glimpse (code_clan_tweets)
```

```{r}
view(code_clan_tweets)
```
#This them gave me the glimpse - worked well

```{r}
str(code_clan_tweets)
```


```{r}
code_clan_tweets
```


```{r}
code_clan_tweets%>%
  filter(is_quote)

```

```{r}
code_clan_tweets%>%
  filter(is_quote)
```
```{r}
code_clan_tweets%>%
  arrange(source)
```

```{r}
code_clan_tweets%>%
  sum (favorite_count)

```



Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).
Count the 