---
title: "R Notebook"
output: html_notebook
---

```{r}
install.packages('wesanderson')
```
```{r}

devtools::install_github('bbc/bbplot')
```

```{r}
library(tidyverse)
library(dplyr)
```

## Load in the data from the codeclan folder.
##Rewview
```{r}

library(CodeClanData)

```

##MVP Part 1
##Q1 Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.
```{r}
CodeClanData::qb_revenue_breakdown
```

```{r}
ggplot(qb_revenue_breakdown)+
  aes( x= Year, y = Revenue, fill = Product)+
  geom_col()+
labs(x= 'Years', y = 'Sales Revenues',
       title = 'Smart Products Revenue Breakdown By Product Type and Year',
       subtitle = 'subtitle',
       fill= 'Product Type',
       caption = 'Sales Team')
   
```
## Actually managed to get the x/y axis resolved
##Got titles in and captions.



```{r}
ggplot(qb_revenue_breakdown)+
  aes( x= Year, y = Revenue, fill = Product)+
  geom_col()
  
```
#Now correct

```{r}
qb_revenue_breakdown%>%
     ggplot(aes( x = Revenue, y = Product, fill= Year))+
  aes(x=Revenue, y = Product)+
  geom_col()
labs(x= 'Revenue', y = 'Product',
       title = 'Revenue Breakdown By Product Type and Year',
       subtitle = 'subtitle',
       fill= 'some title',
       caption = 'Sales Team')
```

##REvenue data needs to be placed in the ggplot
## Finally managed to get this completed - took a long time to complete this but got there is the end.


```{r}
qb_revenue_breakdown%>%
  select(Product, Year)



```
students%>%
  select(school_year, superpower)%>%
  ggplot(aes(x = superpower, fill = school_year))+
  geom_bar(stat = 'count')










