---
title: "R Notebook"
output: html_notebook
---

```{r}
install.packages('wesanderson')
```
```{r}

devtools::install_github('bbc/bbplot')
```

```{r}
library(tidyverse)
```

## Load in the data from the codeclan folder.
##Rewview
```{r}

library(CodeClanData)

```

##MVP Part 1
##Q1 Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.
```{r}
CodeClanData::qb_revenue_breakdown
```

```{r}
CodeClanData::qb_revenue_breakdown%>%
    ggplot(qb_revenue_breakdown =, aes( x = product, y = year))+
  geom_bar(aes(x=Product, y = year))
```




ggplot(students) +
  geom_bar(aes(x = superpower, fill = school_year), position = "dodge")

```{r}
qb_revenue_breakdown%>%
  select(Product, Year)



```
students%>%
  select(school_year, superpower)%>%
  ggplot(aes(x = superpower, fill = school_year))+
  geom_bar(stat = 'count')








```{r}
CodeClanData::qb_monthly_sales
```

```{r}
CodeClanData::qb_device_data
```




