---
title: "Programming in R Homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

# MVP

<br> 

**Question 1.** \
Find the weather forecast for the next three days online.
Create a list of lists in which each inner list should be labelled with the name of the day of the week.
Each inner list should contain named elements telling you the temperature,
chance of rain
and wind speed.


```{r}
weather_info_list <- list(
                "Thur" = list(Temp = 13, chance_of_rain = 4, Wind_speed = 4),
                "Fri" = list(Temp = 11, chance_of_rain = 35, wind_speed = 11),
                "Sat" = list(Temp = 11, chance_of_rain =36, Wind_Speed = 10))
                
```


```{r}
weather_info_list

```
#Not sure in the right format - does not look that tidy and i wanted in inn columns


```{r}
weather_info_list$Thur$chance_of_rain
```



<br>

**Question 2.** \
Using the list you've just made find:

  i. The chance of rain tomorrow Thur 4
  
  iii. The temperature tomorrow.

```{r}
weather_info_list$Thur$Temp
```
#wind speed on Saturday

```{r}
weather_info_list$Sat$Temp
```

#Not correct way to do things

```{r}
weather_info [[1]][[2]]

```
ii. The wind speed on the day after tomorrow - saturday 11
```{r}
weather_info [[2]][[3]]
```
iii. The temperature tomorrow.Thur 13

```{r}

weather_info [[1]][[1]]

```

#wow the furthest I think i have ever got in the homework (smiling face)




<br>

**Question 3.** \
Find a 14 day forecast online and create a matrix of the forecasts for temperature,
where each week is one row and columns correspond to days.

You will want to give a name to the matrix you create.

```{r}
forecast_14_days_vector <- c(14L, 20L, 14L, 11L, 14L, 15L, 16L, 18L, 17L, 13L, 16L, 16L, 
18L, 16L)

forecast_14_days <- matrix(
  forecast_14_days_vector,
  nrow = 2,
  ncol = 7, 
  byrow = TRUE
)

```
```{r}
forecast_14_days
```
```{r}

```
```{r}
cat(letters)
```
```{r}
cat(letters,sep = "\tab")
```
```{r}
cat(LETTERS,sep = "\n")
```


```{r}c
matrix(1:4, nrow = 2, ncol = 7)
```
#so this give me a colume with 2rows (for this weeks) and 7 days for the temperatures. Not really what i wanted to will have another go.


```{r}
matrix(1:14, nrow = 2, ncol = 7)
```


```{r}
Weather_week_one <-c ("week 1", 23,25,45,34,23,56,45)
weather_week_two <-c("Week 2", 34,23,12,14,34,13,13)

```
```{r}
matrix(Weather_week_one) 
matrix(weather_week_two)

```

# AAAAh not sure how to do the rnows and columns - tried to hunt it out,



<br>

**Question 4.** \
From the matrix you just made select:

  i. The third day of the second week
  
```{r}
matrix(weather_week_two)
matrix =(3)
```
  
  
  ii. The whole second week
  iii. The first, third and fifth days in both weeks.

#Moving on to Q6



<br>

**Question 5.** \
Write a function that pre-appends "The answer is: " to any character input, while for numeric input, it either just returns the number for numbers less than 10, or divides the number by 10 for numbers greater than 10. For anything else return "Invalid input".

```{r}

multiply_by_5 <- function(x){
  return(x*5)
}

```
#1.5hours and that is enough for me - bed time.


<br>

**Question 6.** \
Write a function which checks if two vectors have the same elements. 

* If they have the same elements in the same order, return "Exactly the same"
* If they have the same elements but in a different order, return "The same"
* If they don't have the same elements, return "Different".


<details>
<summary>**Hints**</summary>
* You can check if two vectors have the same elements but in a different order by using `sort` to sort each vector first and then checking if they are equal.
* Have a look at the `all()` function
</details>
</blockquote>


# Extension

<br>

**Question 7.** \
Write code that prints a multiplication table for numbers up to 12. i.e. there will be 12 rows and 12 columns, and each element should be the row number multiplied by the column number.

*From: https://adriann.github.io/programming_problems.html*

<br>

**Question 8.** \
Write a function that takes a vector, and creates a text art histogram, like the one below.

You may want to use the function `cat()`. This is similar to `print()`, but prints directly, without vector markers. You can also include newlines `"\n"` when using `cat()`.

For example, the vector
`c(1, 2, 3, 4, 5, 1, 3, 4, 5, 1, 3, 4, 4, 3, 3, 3, 3)`
should produce the histogram below - the histogram dislpays the number of times each number appears in the vector

```{r}
library(stringr)
counts <- matrix(nrow = 9, ncol = 1)
numbers <- sample(1:5, size = 50, replace = TRUE)
art <- function(x){
  for (m in 1:9){
    counts[m] <- sum(str_count(x, pattern = as.character(m)))
    }
  for (num in counts) {
    for (rep in 1:num){
      if(num == 0){
        break
      }
      cat("*")
    }
    if (num != 0)
    cat("\n")
  }
}
art(numbers)
```




```
1 | ***
2 | *
3 | *******
4 | ****
5 | **
```

