---
title: "R Notebook"
output: html_notebook
---

#Purpose of the homework is to create a decision tree to see which factors are useful in predicting whether or not a passenger on the titanic will survive.
#Which factors are useful as the x variable?
#Data Dictionary
sex: Biological Sex, male or female
age_status: adult or child (child defined as under 16)
class : Ticket class, 1 = 1st (Upper class), 2 = 2nd (Middle Class), 3 = 3rd (Lower Class)
port_embarkation: C = Cherbourg, Q = Queenstown, S = Southampton
sibsp : number of siblings / spouses aboard the Titanic
parch: number of parents / children aboard the Titanic. Some children travelled only with a nanny, therefore parch=0 for them.
survived_flag : did they survive, 0 = No, 1 = Yes

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(janitor)
library(fastDummies)
library(GGally)
library(ggfortify)
library(mosaic)
library(mosaicData)

library(tidyverse)
library(readr)
titanic_set <- read_csv('3_homework/data/titanic_decision_tree_data.csv')


shuffle_index <- sample(1:nrow(titanic_set))


titanic_set <- titanic_set[shuffle_index, ]
```
```{r}

```

```{r}
titanic_clean <- titanic_set %>%
  filter(survived %in% c(0,1)) %>%

    mutate(sex = as.factor(sex), 
           age_status = as.factor(if_else(age <= 16, "child", "adult")),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")), 
           survived_flag = factor(survived, levels = c(0,1), labels = c("No", "Yes")), 
           port_embarkation = as.factor(embarked)) %>%
  select(sex, age_status, class, port_embarkation, sib_sp, parch, survived_flag) %>%
  na.omit()
```

```{r}
ggplot(titanic_clean) +
  geom_bar(aes(y = survived, x = class()))
```


```{r}
ggplot(titanic_clean) +
  geom_bar(aes(x = class, fill = survived_flag))
```

#lower class least likely to survive.

```{r}
ggplot(titanic_clean) +
  geom_bar(aes(x = age_status, fill = survived_flag))
```

#inconclusive on this one.


```{r}
ggplot(titanic_clean) +
  geom_bar(aes(x = sib_sp, fill = survived_flag))
```

#Children travelling along with nanny less likely to survive. Only child

```{r}
ggplot(titanic_clean) +
  geom_bar(aes(x = port_embarkation, fill = survived_flag))
```

#Passenger embarking from Southhampton more likely to die - but more got on in Southamption.

#Test Train and SPlit

```{r}
set.seed(19)

# get how many rows we have in total to work out the percentage
n_data <- nrow(titanic_clean)

# create a test sample index
test_index <- sample(1:n_data, size = n_data*0.2)

# create test set
titanic_test  <- slice(titanic_clean, test_index)

# create training set
titanic_train <- slice(titanic_clean, -test_index)
```


```{r}
titanic_test %>%
 janitor::tabyl(survived_flag)
```

```{r}
titanic_train %>%
 janitor::tabyl(survived_flag)
```
#Fair split for this purpose.

#Decision Tree

```{r}
titanic_fit <- rpart(
  formula = survived_flag ~ ., 
  data = titanic_train, 
  method = 'class'
)

rpart.plot(titanic_fit, 
           yesno = 2, 
           fallen.leaves = TRUE, 
           faclen = 6, 
           digits = 4)
```


What variables are important? class of passenger, gender and number of siblings (if a child) 
What does each node tell you?

male/adults most unlikely to survive.
Female passenger travelling along were next least likely to survive.
Chldren with no other siblings and travelling alone/nanny also least likely to survive.

Who has the highest chance of surviving? Women in upper class sections of the boat.

Who has the lowest? men/lower classs section.









