---
title: "R Notebook"
output: html_notebook
---

#Purpose of the homework is to create a decision tree to see which factors are useful in predicting whether or not a passenger on the titanic will survive.
#Which factors are useful as the x variable?
#Data Dictionary
sex: Biological Sex, male or female
age_status: adult or child (child defined as under 16)
class : Ticket class, 1 = 1st (Upper class), 2 = 2nd (Middle Class), 3 = 3rd (Lower Class)
port_embarkation: C = Cherbourg, Q = Queenstown, S = Southampton
sibsp : number of siblings / spouses aboard the Titanic
parch: number of parents / children aboard the Titanic. Some children travelled only with a nanny, therefore parch=0 for them.
survived_flag : did they survive, 0 = No, 1 = Yes

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(janitor)
library(fastDummies)
library(GGally)
library(ggfortify)
library(mosaic)
library(mosaicData)

library(tidyverse)
library(readr)
titanic_set <- read_csv('3_homework/data/titanic_decision_tree_data.csv')


shuffle_index <- sample(1:nrow(titanic_set))


titanic_set <- titanic_set[shuffle_index, ]
```
```{r}

```

```{r}
titanic_clean <- titanic_set %>%
  filter(survived %in% c(0,1)) %>%

    mutate(sex = as.factor(sex), 
           age_status = as.factor(if_else(age <= 16, "child", "adult")),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")), 
           survived_flag = factor(survived, levels = c(0,1), labels = c("Died", "Survived")), 
           port_embarkation = as.factor(embarked)) %>%
  select(sex, age_status, class, port_embarkation, sib_sp, parch, survived_flag) %>%
  
  na.omit()
```

```{r}
ggplot(titanic_clean) +
  geom_bar(aes(x = survived_flag))
```


```{r}
ggplot(titanic_clean) +
  geom_bar(aes(x = class, fill = survived_flag))
```

#lower class least likely to survive.

```{r}
ggplot(titanic_clean) +
  geom_bar(aes(x = age_status, fill = survived_flag))
```

#inconclusive on this one.


```{r}
ggplot(titanic_clean) +
  geom_bar(aes(x = sib_sp, fill = survived_flag))
```

#Children travelling along with nanny less likely to survive. Only child

```{r}
ggplot(titanic_clean) +
  geom_bar(aes(x = port_embarkation, fill = survived_flag))
```

#Passenger embarking from Southhampton more likely to die - but more got on in Southamption.

#Test Train and SPlit

#Model with the set seed section - looks like you must always clarify you are starting the model at a set point in the process.
```{r}
set.seed(19)

# get how many rows we have in total to work out the percentage
n_data <- nrow(titanic_clean)

# create a test sample index
test_index <- sample(1:n_data, size = n_data*0.2)

# create test set
titanic_test  <- slice(titanic_clean, test_index)

# create training set
titanic_train <- slice(titanic_clean, -test_index)
```


```{r}
titanic_test %>%
 janitor::tabyl(survived_flag)
```

```{r}
titanic_train %>%
 janitor::tabyl(survived_flag)
```
#Fair split for this purpose.

#Decision Tree

```{r}
titanic_fit <- rpart(
  formula = survived_flag ~ ., 
  data = titanic_train, 
  method = 'class'
)

rpart.plot(titanic_fit, 
           yesno = 2, 
           fallen.leaves = TRUE, 
           faclen = 6, 
           digits = 4)
```


What variables are important? class of passenger, gender and number of siblings (if a child) 
What does each node tell you?
Top Node - 0.41 survived / 0.58 died

male/adults most unlikely to survive. Survival rate of 0.17
Female passenger/lower class travelling along were next least likely to survive.
Children with a lot of siblings (more than 3)  least likely to survive.0.10 probability

Who has the highest chance of surviving? Women in upper class sections of the boat.

Who has the lowest? men/lower class section.

#Predictors

```{r}
library(modelr)
library(yardstick)
library(caret)
```

```{r}
titanic_test_pred <- titanic_test %>%
  add_predictions(titanic_fit, type = 'class')
```


```{r}
titanic_test_pred %>%
  select(sex,age_status,class,port_embarkation,sib_sp, parch,survived_flag,pred)
```


```{r}
titanic_test_pred <- titanic_test %>%
                 add_predictions(titanic_fit, type = 'class')


conf_mat <- titanic_test_pred %>%
              conf_mat(truth = survived_flag, estimate = pred)
conf_mat
```
#Let’s also see accuracy, TPR (sensitivity) and TNR (specificity)

```{r}
titanic_test_pred %>%
  accuracy(truth = survived_flag, estimate = pred)
```

```{r}
titanic_test_pred %>%
  yardstick::sensitivity(truth = survived_flag, estimate = pred)
```

```{r}
titanic_test_pred %>%
  yardstick::specificity(truth = survived_flag, estimate = pred)
```

```{r}
library(caret)
confusionMatrix(data = titanic_test_pred$pred, reference = titanic_test_pred$survived_flag)  
```

#Accurancy of 0.82

