---
title: "R Notebook"
output: html_notebook
---
#Revision homework on key areas to better undersand.
#list
#select() selects columns vertically 
#filter() + logical operators esp. (!=, ==, %in%) - works horizontally
#& (and), | (or)
#arrange()
#mutate() + changing column data types
#summarise()
#%>% and pulling it all together
#group_by() with summarise() and mutate()
#pull()


```{r}
library(tidyverse)
```
```{r}
books <- read_csv("C:/Users/44792/OneDrive/Desktop/Codeclan 2022/Code-Clan-Homework-Jane-Hogg/week 1/Weekend Homework Week 1/2_weekend_homework/data/books.csv")
View(books)
```
```{r}
books
```

```{r}
books%>%
select(num_pages, authors)
```
```{r}
str(books)
```
```{r}
books%>%
  select(num_pages)%>%
  filter(num_pages < 30)%>%
  count()
  
```
#Practice the select,filter and count verbs
#indicates the number of books with less than 30 pages (a total of 305)
#logical operations too

#mutate() + changing column data types

```{r}
books%>%
  select(num_pages,bookID)
```

#mutate() + changing column data types


```{r}
books%>%
  select(num_pages,bookID,ratings_count)%>%
  group_by(num_pages)%>%
  mutate(num_pages, bookID =bookID*5)
```

#mutate has been used to multiply the ratings_count.  Might be useful if wanted to model an increase of a figure?


#summarise()

```{r}
books%>%
  summarise(authors, publication_date,publisher)

```

#group_by() with summarise() and mutate()

```{r}
books%>%
  summarise(authors, publication_date,publisher)
  mutate(authors, publisher == "crown")
```
~Note sure that this worked that well

```{r}
books %>%
  filter(!is.na(language_code))%>%
 
```

#pull

Calculate the average rating count for all books and create a new column which states TRUE if the average rating for all books is above this average

```{r}
average_ratings_count <- books %>%
  summarise(average_rating = mean(ratings_count, na.rm = TRUE))
  
```

#created the new variable of average rating count 17942


