---
title: "R Notebook"
output: html_notebook
---
#Revision homework on key areas to better undersand.
#list
#select() selects columns vertically 
#filter() + logical operators esp. (!=, ==, %in%) - works horizontally
#& (and), | (or)
#arrange()
#mutate() + changing column data types
#summarise()
#%>% and pulling it all together
#group_by() with summarise() and mutate()
#pull()


```{r}
library(tidyverse)
```
```{r}
books <- read_csv("C:/Users/44792/OneDrive/Desktop/Codeclan 2022/Code-Clan-Homework-Jane-Hogg/week 1/Weekend Homework Week 1/2_weekend_homework/data/books.csv")
View(books)
```
```{r}
books
```

```{r}
books%>%
select(num_pages, authors)
```
```{r}
str(books)
```
```{r}
books%>%
  select(num_pages)%>%
  filter(num_pages < 30)%>%
  count()
  
```
#Practice the select,filter and count verbs
#indicates the number of books with less than 30 pages (a total of 305)
#logical operations too
##count functions select = 

```{r}

books%>%
  select(num_pages)%>%
  filter(num_pages < 30)%>%
  summarise(low_page_count = n())
```
##summarise groups the select and filter and then gives (if required) better title for the outcome of the data column.



#mutate() + changing column data types

```{r}
books%>%
  select(num_pages,bookID)
```

#mutate() + changing column data types


```{r}
(books_5 <-books%>%
  select(num_pages,bookID,ratings_count)%>%
  group_by(num_pages)%>%
  mutate( bookid_5 =bookID*5))
```

#mutate has been used to multiply the ratings_count.  Might be useful if wanted to model an increase of a figure?
#booksid_5 < this assigns (saves this function output and it can be called again wit not needs to write the code)
##place the assigned bookis_5 with a () an output to see.



```{r}
(books_5 <-books%>%
  select(num_pages,bookID,ratings_count)%>%
  group_by(num_pages)%>%
  mutate( bookid_5 =bookID*5, .after = "bookID"))
```

##placing the mutate function with .after = the column you have mutated.
##can also use .before 

```{r}
(books_5 <-books%>%
  select(num_pages,bookID,ratings_count)%>%
  group_by(num_pages)%>%
  mutate( bookid_5 =bookID*5, .after = "bookID"))%>%
  mutate(num_pages = as.integer(num_pages))
```

##process above changes the type of date and into an interger.
##interger = from a double (and this column is only going to have whole numbers)
##changing the data type can be helpful in later stages of the course.



#summarise()

```{r}
books%>%
  summarise(authors, publication_date,publisher)

```

#group_by() with summarise() and mutate()

```{r}
books%>%
  summarise(authors, publication_date,publisher)
  mutate(authors, publisher == "crown")
```
###Note sure that this worked that well
##sumarise - usually looking for a mathimatical aggregation of the date
##group by

```{r}
books %>%
  filter(!is.na(language_code))%>%
 
```

#pull

Calculate the average rating count for all books and create a new column which states TRUE if the average rating for all books is above this average

```{r}
books%>%
mutate(average_ratings_count = if_else
       (ratings_count > mean(ratings_count), TRUE, FALSE),
       .after = ratings_count)

```
##add a extra () at beginning and end gives you an output
##if else within a mutate function
##when see create new column need to mutate

#created the new variable of average rating count 17942


