---
title: "R Notebook"
output: html_notebook
---

#Q1 Load the data.

```{r}
library(tidyverse)
library(janitor)
library(gtools)

```

```{r}
library(readr)
X20190928_items <- read_csv("data/20190928-items.csv")
View(X20190928_items)
```
```{r}
phone_data <-(X20190928_items)
```

```{r}
phone_data %>%
  select(brand)
 
```

```{r}
phone_data%>%
  count(brand)
 
```
#count and then need this is desc order.
```{r}
phone_data%>%
  count(brand)%>%
  arrange(desc(n))
```

#Q2The brand with the highest numbers of phones in the dataset is samsung with 397 phones.


```{r}
samsung_data <- phone_data%>%
  filter(brand == "Samsung")
```

Q3For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?



```{r}
review_frequency <-samsung_data %>%
  tabyl(totalReviews)

```

#total time that the data occurs for the review of the phone.
#Now plotting the probability distribution

```{r}
review_frequency %>%
  ggplot(aes(x=totalReviews, y=percent))+
  geom_col()+
  theme_linedraw()
```
#Need to look at summarise of the distribution as this is not that great a graph.
#need the mean/median/mode

```{r}
get_mode <- function(data){

  tabled_data <- table(data)
  table_names <- names(tabled_data)
  
  return( table_names[tabled_data == max(tabled_data)] )
  
}
```

```{r}
review_frequency%>%
  summarise(mean_daily_reviews = mean(totalReviews), 
            median_daily_reviews = median(totalReviews),
            mode_daily_reviews = get_mode(totalReviews))
  
```






air_con_sales %>%
  summarise(mean_daily_sales = mean(units_sold), 
            median_daily_sales = median(units_sold),
            mode_daily_sales = get_mode(units_sold))
