---
title: "R Notebook"
output: html_notebook
---

#Q1 Load the data.

```{r}
library(tidyverse)
library(janitor)
library(gtools)

```

```{r}
library(readr)
X20190928_items <- read_csv("data/20190928-items.csv")
View(X20190928_items)
```
```{r}
phone_data <-(X20190928_items)
```

```{r}
phone_data %>%
  select(brand)
 
```

```{r}
phone_data%>%
  count(brand)
 
```
#count and then need this is desc order.
```{r}
phone_data%>%
  count(brand)%>%
  arrange(desc(n))
```

#Q2The brand with the highest numbers of phones in the dataset is samsung with 397 phones.


```{r}
samsung_data <- phone_data%>%
  filter(brand == "Samsung")
```

Q3For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?
#Probability density was the action


```{r}
review_frequency <-samsung_data %>%
  tabyl(totalReviews)

```

#total time that the data occurs for the review of the phone.
#Now plotting the probability distribution
#There isn't a percent column in the table. Error at this point on the y axis.

```{r}
review_frequency %>%
  ggplot(aes(x=totalReviews, y=percent))+
  geom_col()+
  theme_linedraw()
```
#Need to look at summarise of the distribution as this is not that great a graph.
#need the mean/median/mode

```{r}
get_mode <- function(data){

  tabled_data <- table(data)
  table_names <- names(tabled_data)
  
  return( table_names[tabled_data == max(tabled_data)] )
  
}
```

```{r}
review_frequency%>%
  summarise(mean_daily_reviews = mean(totalReviews), 
            median_daily_reviews = median(totalReviews),
            mode_daily_reviews = get_mode(totalReviews))
  
```

#distribution shape might look better - as this looks wild.

```{r}
review_frequency %>%
  ggplot(aes(x=totalReviews))+
  geom_histogram(col = "red")
  
```

#bimodal distribution as a bit of a peak again at 500 reviews

#Range Refresh
```{r}
range_reviews <-review_frequency %>%
  summarise(range_reviews = range(totalReviews))
```
1 - 980
#outliers - ???

#Quartile and interquartile

```{r}
review_frequency%>%
  group_by(totalReviews)
 
```






```{r}
review_frequency %>%
  summarise(
    num = n(),
    mean = mean(totalReviews),
    sd = sd(totalReviews)
  )
  
```

#code provides the mean and the sd = standard normal that can then be plotted.

```{r}
samsung_data <- phone_data %>%
  filter(brand == "Samsung") %>%
  select(rating)

samsung_stats <- phone_data %>%
  filter(brand == "Samsung") %>%
  summarise(
    count = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
samsung_stats

```
# From 397 ratings there is on average a review of 3.5733 and deviation of 0.68 deviation from the average.
#Filter for a number of ratings 

```{r}
samsung_data %>%
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white") +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = samsung_stats$mean,
      sd = samsung_stats$sd
    ),
    col = "red"
  )
```


```{r}
samsung_data %>%
  filter(rating  > 10) % %
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white") +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = samsung_stats$mean,
      sd = samsung_stats$sd
    ),
    col = "red"
  )
```
```











