---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(fastDummies)
library(GGally)
library(ggfortify)
library(mosaic)
library(mosaicData)
```


```{r}
library(readr)
housing_prices <- read_csv("4_homework/data/housing_prices.csv")
View(housing_prices)
```

```{r}
housing_prices%>%
  clean_names()
```


#1 We expect the total_rooms of houses to be strongly correlated with total_bedrooms. Use ggpairs() to investigate correlations between these two variables.


```{r}
rooms_bedrooms <- housing_prices %>%
  select(total_rooms, total_bedrooms)
```



```{r}
library(GGally)
ggpairs(rooms_bedrooms) + theme_grey()
```

##strong correlation between the number of bedrooms and the number of rooms overall.

##So, we do find significant correlations. Let’s drop total_bedrooms from the dataset, and use only total_rooms going forward.


```{r}
housing_pricestrimmed <-housing_prices%>%
  select(-c (total_bedrooms))  
  
```

```{r}
library(GGally)
ggpairs(housing_pricestrimmed) + theme_grey()
```

##That looks a mess - loads of blobs and not sure what it is showing.


We are interested in developing a regression model for the median_house_value of a house in terms of the possible predictor variables in the dataset.

Use ggpairs() to investigate correlations between median_house_value and the predictors (this may take a while to run, don’t worry, make coffee or something).

```{r}
housing_pricestrimmed %>%
  ggplot(aes(median_house_value,ocean_proximity)) + 
  geom_boxplot()
```
##oriximity to the ocean is the variable that is more likely to impact on the value of  property

```{r}
housing_pricestrimmed%>%
  ggpairs(median_house_value,ocean_proximity)+theme_grey()
```

```{r}
housing_pricestrimmed %>%
  ggplot(aes(median_house_value, oceanprox))+
  geom_point()
  
```


```{r}
