---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(fastDummies)
library(GGally)
library(ggfortify)
library(mosaic)
library(mosaicData)
```


```{r}
library(readr)
housing_prices <- read_csv("4_homework/data/housing_prices.csv")
View(housing_prices)
```

```{r}
housing_prices%>%
  clean_names()
```


```{r}
glimpse(housing_prices)
```


#1 We expect the total_rooms of houses to be strongly correlated with total_bedrooms. Use ggpairs() to investigate correlations between these two variables.

## Firstly looked at developing some other bedrooms
```{r}
bear_in_house <-housing_prices %>%
  mutate(bedrooms_per_house = total_bedrooms/households,
         rooms_per_house = total_rooms/households,
         people_per_house = population/households,
         bedrooms_per_house = total_bedrooms/population,
         rooms_per_house = total_rooms/population,
         bedrooms_per_house = total_bedrooms / total_rooms,
         non_bedrooms_per_house = rooms_per_house- bedrooms_per_house)
```
```{r}
glimpse(bear_in_house)
```


```{r}
ggpairs1 <-bear_in_house%>%
  select(median_house_value,
         housing_median_age,
         ocean_proximity,
         median_income)%>%
  ggpairs()%>%


```



```{r}
ggpairs2 <-bear_in_house%>%
  select(median_house_value,
         total_rooms,
         rooms_per_house,
         total_bedrooms,
         bedrooms_per_house)%>%
ggpairs()

```


```{r}
ggpairs3 <-bear_in_house%>%
  select(median_house_value,
         )
```


```{r}
bear_in_house%>%
  count(ocean_proximity)
```

```{r}
bear_in_house%>%
  select(ocean_proximity, median_house_value)

```



```{r}
rooms_bedrooms <- housing_prices %>%
  select(total_rooms, total_bedrooms)
```



```{r}
library(GGally)
ggpairs(rooms_bedrooms) + theme_grey()
```

## strong correlation between the number of bedrooms and the number of rooms overall.

## correlations and coefficient - 1 - 0 - so anything close to 1 then strong correlation.

## coefficnet is a number that expresses a measurment of a particular quantity of a substance or object.

##So, we do find significant correlations. Let’s drop total_bedrooms from the dataset, and use only total_rooms going forward.


```{r}
housing_pricestrimmed <-housing_prices%>%
  select(-c (total_bedrooms))  
  
```

```{r}
library(GGally)
ggpairs(housing_pricestrimmed) + theme_grey()
```

##That looks a mess - loads of blobs and not sure what it is showing.


We are interested in developing a regression model for the median_house_value of a house in terms of the possible predictor variables in the dataset.

Use ggpairs() to investigate correlations between median_house_value and the predictors (this may take a while to run, don’t worry, make coffee or something).


```{r}
ggpairs(housing_pricestrimmed)
```


```{r}
housing_pricestrimmed %>%
  ggplot(aes(x = median_income, y = median_house_value)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

##so do produce a number of plots to look at the predictable variable.

```{r}
housing_pricestrimmed %>%
  ggplot(aes(x = latitude, y = median_house_value)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
##keep the Y axis constant (median house value) and then change the x axis.
```{r}
housing_pricestrimmed%>%
  ggplot(aes(x = ocean_proximity, y = median_house_value)) +
  geom_boxplot()
```

##This was wrong below - look at the section above.

```{r}
housing_pricestrimmed %>%
  ggplot(aes(median_house_value,ocean_proximity)) + 
  geom_boxplot()
```


```{r}
housing_pricestrimmed %>% 
  distinct(ocean_proximity)
```

#4 dummy predictors

```{r}
housing_pricestrimmed %>%
  ggplot(aes(x = housing_median_age, y = median_house_value)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
mod1 <- lm(median_house_value ~ median_income,
           data = housing_pricestrimmed)

summary(mod1)
```
##intercept of the house values is £45k
##median income of £39k


```{r}
autoplot(mod1)
```


```{r}
mod2<- lm(median_house_value ~ ocean_proximity,
           data = housing_pricestrimmed)

summary(mod2)

 
```


```{r}
mod3<- lm(median_income ~ ocean_proximity,
           data = housing_pricestrimmed)

summary(mod3)
```



```{r}
ggplot(housing_pricestrimmed, aes (x = median_income))+
  geom_histogram()
```










