---
title: "R Notebook"
output: html_notebook
---


```{r}
install.packages('wesanderson')


```
```{r}
```


```{r}
library(tidyverse)
```


```{r}
```
```{r}
devtools::install_github('bbc/bbplot')
```
```{r}

library(ggplot2)
library(CodeClanData)
library(dplyr)
library(janitor)
library(devtools)

```

```{r}
CodeClanData::game_sales
```

```{r}
view(game_sales)
```


```{r}
ggplot(game_sales)+
  aes(
    x = critic_score,
    y = user_score
  ) +
  geom_point() + 
  labs(x = "Critics Score", y = "Gamer Score",
       title = 'Critics Score v Gamer Score',
       subtitle = 'November 2022',
       caption = 'Game Sales Team, Edinburgh')
```
##Bit dull. Revise the colour section on the notes and enhance this


```{r}
ggplot(game_sales)+
  aes(
    x = critic_score,
    y = user_score
  ) +
  geom_point() + 
  scale_color_gradient( low = "steel blue", high = "dark blue")+
  labs(x = "Critics Score", y = "Gamer Score",
       title = 'Critics Score v Gamer Score',
       subtitle = 'November 2022',
       caption = 'Game Sales Team, Edinburgh')
  

```

```{r}
ggplot(game_sales) +
  aes(x = critic_score) +
  geom_histogram(bins = 80, col = "white", fill = "dark blue") + 
  theme_light() + 
  labs(y = "Sales", x = "Critic Score")
```

#Higher the critic score the higher th volume of sales

```{r}
ggplot(game_sales)+
  geom_line(aes(x=year_of_release, y = sales, colour = genre))

```

#looks a bit crowded
#Need to add some titles

```{r}

ggplot(game_sales)+
  geom_line(aes(x=year_of_release, y = sales, colour = genre))+
labs(x= 'Year of Release', y = 'Sales',
       title = 'Year of Release and Games Genre',
       subtitle = 'Twenty Years of Gaming',
       fill= 'some title',
       caption = 'Games Sales Team, Edinburgh, November 2022')
```


```{r}
 ggplot(game_sales)+
  geom_bar(aes(x = genre, fill = year_of_release), stat = "count")
  

```

```{r}
ggplot(game_sales) +
  geom_bar(aes(x = genre, fill = year_of_release)) +
  labs(x = "Genre",
    y = "Number Released",
    title = "Preferred Genre by Year of Release",
    subtitle = "Games Genre ",
    fill = "Year of Release")
```

```{r}
ggplot(game_sales) +
  theme_classic()+
  geom_bar(aes(x = genre, fill = year_of_release)) +
  
  labs(x = "Genre",
    y = "Year of Release",
    title = "Preferred Genre by Year of Release",
    subtitle = "Games Genre ",
    fill = "Year of Release")+
  coord_flip()


```

##Looks a lot better but wanted to highlight the sport/action with colour.



    

```{r}

```

```{r}
ggplot(game_sales) +
  theme_classic()+
  geom_bar(aes(x = publisher, fill = developer)) +
  labs(x = "Publisher",
    y = "No. Games",
    title = "Publisher and Developer Profile",
    subtitle = "Games Genre ",
    fill = "Top Developer")+
coord_flip()
```




#building the app and what to focus on.

##What insights to highlight - what is most popular genre?
##What should the users actionable insights be - what type of genre will generate the most revenue.?
##Which developer to select based on sales success.?







