---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
library(CodeClanData)
library(dbplyr)
```

# Loaded the Data in to R and also into Computer etc.

```{r}
books
```

#checking the data set - 13 columns of data - rowID, bookID, Title,author, average rating,isbn, (two of these), language, number of pages, rating count, text review count, publised date and then publisher.
```{r}
ncol(books)
```
```{r}
dim(books)
```
# A total of 11,123 books listed in the dataset.

```{r}
names (books)
```

#running the first 10 rows to follow the lesson plan on day 2
```{r}
head(books,10)
```
```{r}
tail(books,10)
```


```{r}
glimpse(books)
```

#Love this format of the data.
```{r}
view(books)
```

#Practice the Select function - Going to look at some authors to see how many books they have published.


```{r}

select(books)
  
```

```{r}
books %>%
  select(authors)
```

# Not - going to try and work out what is wrong with this (done an hour)
#yipee worked it out as needed the pipe !!


```{r}
books %>%
  select(authors,language_code,publication_date)
```

```{r}
books %>%
  select(authors,average_rating)
```
#Trying to look at authors with average rating more than 3
```{r}
books
```

```{r}
library(dplyr)

```
```{r}
books
```


  chinesemeal%>%
  group_by(Year) %>%
  mutate(AnnualCalsPerDay = sum (CaloriesPerDay)) %>%
  arrange(Year)
```{r}
books%>%
group_by(authors)
```
#see that i can a group in the tibble that is 6639


```{r}
books%>%
group_by(language_code)
```

#second table that is language code (27)

```{r}
books%>%
group_by(publisher)
```

#can see have tabel of publishers 2290 - a lot more that expected.


drinks_content %>%
  select(Beverage_category, Beverage, Beverage_prep, Calories) %>%
  filter(is.na(Calories)) %>%
  summarise(count_of_missing_calories = n())

```{r}
library(dbplyr)
```


```{r}
books %>%
  Select(num_pages, ratings_count) %>%
  filter(is.na (num_pages)) %>%
  summarise(count_of_missing_pages = n())
  
```

#Frustrated that i can't get the select function to work and have also looked at Youtube



  
```{r}
books%>%
    group_by(ratings_count)%>%
  summarise(mean_rating = mean(ratings_count)) %>%
  arrange(desc(ratings_count))
  
  
 )
```

 # Not sure what I can't get the filter on this with author
 
 
 

```{r}
books%>%
group_by(title)
```
 
 What did i want to do and not achieve?
 Select and filter
 Wanted to look at largest v smallers page numbers
 wanted to look at any link/trend between highest rating and the number of page numbers - to answer the question what is the optimum page numbers v rating.