---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
library(CodeClanData)
```

# Loaded the Data in to R and also into Computer etc.

```{r}
books
```

#checking the data set - 13 columns of data - rowID, bookID, Title,author, average rating,isbn, (two of these), language, number of pages, rating count, text review count, publised date and then publisher.
```{r}
ncol(books)
```
```{r}
dim(books)
```
# A total of 11,123 books listed in the dataset.

```{r}
names (books)
```

#running the first 10 rows to follow the lesson plan on day 2
```{r}
head(books,10)
```
```{r}
tail(books,10)
```


```{r}
glimpse(books)
```

#Love this format of the data.
```{r}
view(books)
```

#Practice the Select function - Going to look at some authors to see how many books they have published.


```{r}

select(books)
  
```

```{r}
books %>%
  select(authors)
```

# Not - going to try and work out what is wrong with this (done an hour)
#yipee worked it out as needed the pipe !!


```{r}
books %>%
  select(authors,language_code,publication_date)
```

