---
title: "R Notebook"
output: html_notebook
---

##Q1 Load in the varies packageas correctly
##read in the date from codeclan
```{r}
library(tidyverse)
library(ggplot2)
library(CodeClanData)
library(dplyr)
library(janitor)
```

```{r}
CodeClanData::backpack
janitor(clean_names)
```

```{r}
view(backpack)
```

##q2Question 2.

##What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

#Distribution of information (packweights) but one variable that that is a constant
##Selected first to provide only one part of the data
 
```{r}

backpack_weight <-backpack%>%
  select(backpack_weight)

```

```{r}
```


```{r}
ggplot(backpack_weight)+
aes((x=outcome))+
  geom_histogram(binwidth = 30,col = "white" )+
  labs(x = "Outcome",
      y= "Count")
```
##No idea why this is not working - will return to this one.

```{r}
¶
```
##AAAAAAAAAAH

```{r}
ggplot(backpack)+
  aes(
    x = backpack_weight,
    y = body_weight
  ) +
  geom_point() + 
  labs(x = "Backpack Weight", y = "Body Weight",
       title = 'Backpack Weight v Body Weight',
       subtitle = 'November 2022',
       caption = 'Child Health Team, Edinburgh')

  
```


##Q 3 Are there differences in backpack weight between sex?
##
```{r}
backpack%>%
  group_by(backpack_weight, sex)%>%
  mutate(mean_group_score = mean(backpack_weight))%>%
  mutate(group = as_factor(group))%>%
  ggplot()+
  aes(x= backpack_weight, y = sex)
```

```{r}
backpack%>%
  group_by(backpack_weight, sex)+
  ggplot()
  aes(x= backpack_weight, y = sex)
ggplot()+
```



```{r}
backpack%>%
  ggplot()+
  geom_line(aes (x= sex, y=backpack_weight, colour = year)) +
  labs(x = "Backpack Weight", y = "Sex",
       title = 'Backpack Weight v Body Weight',
       subtitle = 'November 2022',
       caption = 'Child Health Team, Edinburgh')
```
##Not the best looking graph but you can see that males backpacks are heavier that the females.

##Q4What is the relationship between body weight and backpack weight?
##column plot here to show the comparisons


```{r}
backpack%>%
  ggplot(aes (x = body_weight, y = backpack_weight, colour = sex))+
  geom_point(aes(colour = sex))+
  geom_point( aes(shape = status))+
labs(x = "Body Weight", y = "Backpack Weight",
       title = 'Backpack Weight v Body Weight',
       subtitle = 'November 2022',
       caption = 'Child Health Team, Edinburgh')
```

##Q5 Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

##Q6
##What proportion of students report back pain?
##  Pie Chart - but too late to continue now.








