---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
library(ggplot2)
```

```{r}
library(readr)
transactions <- read_csv("1_weekend_homework/data/online_retail_subset.csv")
View(online_retail_subset)
```

```{r}
head(transactions, 20)
```

Q1 Item A - ‘HEART OF WICKER SMALL’ (StockCode 22469)


```{r}
total_transaction <- transactions%>%
  count()
```


```{r}
transactions%>%
  count(StockCode)%>%
  

  
```

```{r}
 false_white <-transactions%>%
  mutate(StockCode = StockCode %in% c("22469"))

```

```{r}
heart_of_wicker <-transactions%>%
  filter(StockCode ==22469)
  
  
```

```{r}
heart_of_wicker%>%
  count()
```
```{r}
heart_of_wicker%>%
  count(UnitPrice)
```


##Support for Product A = From a total of 30,000 transactions Item 22469 constitutes (110 transaction) 0.3% of the total transactions.
But this is not units or revenue (see above)


##Calculate the support and confidence for rule (A→B).


item A - ‘HEART OF WICKER SMALL’ (StockCode 22469)
item B - ‘LARGE CAKE TOWEL PINK SPOTS’ (StockCode 21110)


```{r}
large_cake <-transactions%>%
  filter(StockCode ==21110)
```
##Support for Product A 22469 (110)  and B 21110 (14) a total of 124 transactions from 30,000 is 1.2% of total transactions - but this does not include number of units or the revenue from the transactions. 




