---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
library(ggplot2)
```
```{r}
msleep <-(data.frame(msleep))
```

##Q1 Jabberwockies (fantasy scary animal created by Lewis Carol ) sleeps for around 7 hours a night, on average. 
##Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.
##Mean sample for all animals v jabberwocky 7 hours

```{r}
mean_sleep <- msleep%>%
  select(sleep_total)%>%
   summarise(
    mean = mean(sleep_total),
    sd = sd(sleep_total))
```
##mean 10.4 and the standard deviation 4.4.
##mean for all animals is 10.4 v jabberwocky at 7hours.
##Sample does differ - visualalise



##Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

```{r}
msleep%>%
  count(vore)
 

    
    
```

```{r}
msleep%>%
  select(vore, sleep_total)%>%
  filter(vore == c("carni", "omni"))
  
```

```{r}

```




```{r}
carni_sleep <- msleep%>%
  select(vore, sleep_total)%>%
  filter(vore == c("carni"))
```

##Now create the mean
```{r}

carni_sleep%>%
 summarise(
    mean = mean(sleep_total),
    sd = sd(sleep_total))
```
##carni animals sleep on average 10.3 hours with an sd of 4.66


```{r}
msleep%>%
  select(vore, sleep_total)%>%
  filter(vore == c("carni", "omni"))
```

```{r}

ggplot(msleep) +
  aes(vore, sleep_total, colour = "red") +
  geom_point()+
  labs(x = "Diet")+
  labs (y = "Total hours sleep in 24hrs",)+
  coord_flip()
```


```{r}

```



```{r}
omni_sleep <- msleep%>%
  select(vore, sleep_total)%>%
  filter(vore == c("omni"))
```


##GGplot Revision




```{r}
ggplot(omni_sleep) +
  aes(x = vore, y = sleep_total, colour = "coral") +
  geom_line()+
  geom_point()
  labs (x = "Diet", Y= "Total Hours Asleep in 24Hrs")+
    theme_classic()
```
##

##Now create the mean

```{r}
omni_sleep%>%
 summarise(
    mean = mean(sleep_total),
    sd = sd(sleep_total))
```
omni animals sleep on average 10.9 hours with an sd of 2.9

Answer
omnivores sleep on average 10.9 hours
herbivores, on average 10.3 hours - think it should be more complicated that this and should really be abe to do a graph for this too.



Q4 Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.

```{r}
msleep%>%
  count(conservation)

```



```{r}
msleep%>%
  filter(conservation == c("domesticated"))

```

##10 domesticated and 83 not domesticated - domesticatd animals orms 12% of the total population.
Now need to try and do that in code.



Q 1.2
You work for a independent coffee shop. The boss tells you that she thinks that around 40% of people in the town (population 30,000) know of the coffee shop, but you are skeptical of the estimate. You conduct a random survey of 200 people in the town, asking if respondents are aware of your coffee shop. You want to use the sample to test the hypothesis that 40% or more of the town’s population have heard of the coffee shop.

Hypothesis Test

Estimated that 40% of the 30,000 population aware of the coffee shop (12,000 people)

Sample of 200
HO - 

xxxxx

```{r}

                )


