---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(janitor)
library(infer)
```



```{r}
library(readr)
ames <- read_csv("7_homework/data/ames.csv")
View(ames)
```



```{r}
skimr::skim(ames)
```

```{r}
ames <-clean_names(ames)
```

```{r}
view(ames)
```

##Q1 Load data and become familiar with it.

##Q2Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?


```{r}
summary_lot_area <- ames%>%
  summarise(
    mean_lot_area = mean(lot_area)
  )

summary_lot_area
```

```{r}
ames%>%
ggplot (aes(x = lot_area))+
  geom_histogram(bins = 150, col = "white", fill = "steelblue")
  
```
##Graph looks a bit odd - tried changing the bins - but looks ok (ish)


```{r}
ames %>%
  ggplot(aes(x = lot_area)) +
  geom_boxplot()
```






#Q3Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
bootstrap_distn <- ames %>%
  specify(response = lot_area) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_distn %>%
  visualise(bins = 30)
```






```{r}
infer_sample <- ames %>%
  specify(response = lot_area)%>%
  generate(reps = 5000, type = "bootstrap")%>%
  calculate(stat = "mean")
```
```{r}
ames%>%
  count(Lot.Area)
```

```{r}
mean_lot_area <-ames%>%
  select(lot_area)%>%
  summarise(
    count = n(),
    mean = mean(lot_area),
    sd = sd(lot_area)
  )

mean_lot_area
```
#Q4  Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution


```{r}
lot_area_ci95 <- bootstrap_distn %>%
  get_ci(level = 0.95, type = "percentile")
lot_area_ci95
```


```{r}
bootstrap_distn %>%
  visualise(bins = 30) +
  shade_ci(endpoints = lot_area_ci95)
```




```{r}
mean_lot_area %>%
ggplot(aes(x= lot_area))+
  geom_histogram(aes(y = ..density..), col= "white")+
  stat_function(
    fun = dnorm,
    args = list(
      mean = lot_area$mean,
      sd = lot_area$sd
    ),
    col = "red"
  )

```
##







