---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(tidytext)
```





```{r}
library(janeaustenr)
```
#how to remove - stop words.   What are stop words.
#These are the, is, are - they allow analysis of the most important words.




```{r}
head(prideprejudice, 30)
```

```{r}
pride_book <- tibble(
  id= 1:length(prideprejudice),
  text = prideprejudice
) %>%
  unnest_tokens(word, text)
pride_book
```



```{r}
pride_book %>%
  group_by(word) %>%
  summarise(
    count = n()
  ) %>%
  arrange(desc(count))
```

#Most commen word ( with the stop words) is the.

## why not make a wordle....

```{r}
unnest_tokens(word,text)
pride_book
```


```{r}
pride_book %>%
  group_by(word)
```
```{r}
ggplot(pride_book, aes(label = word, size = id, colour = word)) +
  geom_text_wordcloud_area(rm_outside = TRUE) +
  scale_size_area(max_size = 20) +
  theme_minimal()
```





```{r}
sense_book <- tibble(
  id= 1:length(sensesensibility),
  text = sensesensibility
) %>%
  unnest_tokens(word, text)
sense_book
```



```{r}
sense_book %>%
  group_by(word) %>%
  summarise(
    count = n()
  ) %>%
  arrange(desc(count))
```

~Most common word in sense and sensibility is to (4116) words


```{r}
sense_book %>%
  anti_join(stop_words)%>%
  count(word, sort = TRUE)
```


#Most common word with out the stop words is Elinor (623)



```{r}
pride_book %>%
  anti_join(stop_words)%>%
  count(word, sort = TRUE)
```

#Most common words (minus the stop words) is Elizabeth at (597)



##sentiment analysis - what is this?
E1motional analysis and the voice of the customer text analysis from reviews or product information or through msg and also what is posted on other social media.
sentiment analysis in risk and medical

```{r}
library(tidytext)
library(janeaustenr)
library(tidyverse)
library(textdata)
```
```{r}
get_sentiments("afinn")
```

```{r}
get_sentiments("bing")
```

```{r}
get_sentiments("loughran")
```


```{r}
get_sentiments("loughran")%>%
  count(sentiment, sort = TRUE)
```


```{r}
get_sentiments("nrc")%>%
  count(sentiment, sort = TRUE)
```

```{r}
library(remotes)
install_github("EmilHvitfeldt/textdata")
install_github("juliasilge/tidytext")
```

```{r}
library(tidytext)
get_sentiments("nrc")
```



```{r}
book_pride <- tibble(
text = prideprejudice,
sentance = 1:length(prideprejudice))%>%
  unnest_tokens(word,text)%>%
  anti_join(stop_words)
```
```{r}
book_pride %>%
  inner_join(get_sentiments("bing"))
```

#analysis of the words in relation to the sentiment of the word in the nvel.


```{r}
books_sentiments <- book_pride%>%
  inner_join(get_sentiments("bing"))
```

```{r}
books_sentiments <- book_pride%>%
  inner_join(get_sentiments("bing"))
books_sentiments %>%
  filter(sentiment == "positive")%>%
  count(word, sort = TRUE)
  
```

```{r}
books_sentiments <- book_pride%>%
  inner_join(get_sentiments("bing"))
books_sentiments %>%
  filter(sentiment == "negative")%>%
  count(word, sort = TRUE)
```

~most positive negative word in Pride and Preduice is love and the most negative is miss.



```{r}
library(janeaustenr) 
sense_book
```



```{r}
books_sentiments <- sense_book%>%
  inner_join(get_sentiments("loughran"))
books_sentiments %>%
  filter(sentiment == "positive")%>%
  count(word, sort = TRUE)
```

```{r}
books_sentiments <- sense_book%>%
  inner_join(get_sentiments("loughran"))
books_sentiments %>%
  filter(sentiment == "negative")%>%
  count(word, sort = TRUE)
```

```{r}
books_sentiment <- sense_book%>%
  filter(is.na(sentiment))%>%
  count(word, sort = TRUE)
```





##summary of the whole range of words as eitehr positive or negative

```{r}
book_sentiments <-book_pride %>%
  inner_join(get_sentiments("afinn"))
```

```{r}
sentance_sentiments <- book_sentiments %>%
  group_by(sentance)%>%
  summarise(
    mean_sentiment = mean(value)
  )
```



```{r}
sentance_sentiments <- book_sentiments %>%
  group_by(sentance)%>%
  summarise(
    mean_sentiment = mean(value)
  )

sentance_sentiments
```

```{r}
ggplot(sentance_sentiments)+
  aes(x = sentance, y = mean_sentiment)+
  geom_point(alpha = 0.1)+
  geom_smooth()
```






