---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
library(fastDummies)
library(GGally)
library(ggfortify)
library(mosaic)
library(mosaicData)
library(leaps)
library(caret)
```



## Average Price Of Avocadoes - Regression Model in relation to Price 2015 - 2018 

## Background

External data showing that Avacadoes are at the lowest price in 5 years and there is both a over supply from Peru/Columbia combined with consumers cuttin back on what is perceived as a high value item.
https://www.foodandwine.com/avocado-surplus-lower-prices-2022-6825177

https://www.freshfruitportal.com/news/2022/07/29/avocado-prices-fall-sharply-in-u-s-amid-heavy-peruvian-supply/

##Date Preparations


```{r}
library(readr)
avocado <- read_csv("1_weekend_homework_part1/data/avocado.csv")
View(avocado)
```
```{r}
glimpse(avocado)
```

```{r}
janitor::clean_names(avocado)
```



```{r}
avocado_clean <-avocado%>%
  clean_names()
```


```{r}
avocado_clean%>%
  skimr::base_skimmers(avocado_clean)
```


```{r}
view(avocado_clean)
```

##Removed the bags and date so that we are able to concentrate on the average price and the volume of individual avocadoes purchased. Reduced to 9 variable now.
##Could have done Train - Test - split at this point

```{r}
avocado_trim<- avocado_clean %>%
  drop_na() %>%
  select(-total_bags, -x_large_bags,-large_bags,-small_bags,-date, -region, -x1)
```

```{r}
dim(avocado_trim)
```


##Building the model - First Predictor - Aim is to build a regression model for the `price` response variable in terms of the multiple potential predictors held in the data frame. I have reduced this to 9 variable


```{r}
avocado_trim %>%
  ggpairs()
```

##Amongst the continuous predictors we see here that x4770 (large Hass Avocado/Type/Time of the year) has some association with the price.

##Building the models
##PLU4770 = large avocado

```{r}
mod1 <- lm(average_price ~ x4770, data = avocado_trim)
summary(mod1)
```
```{r}
par(mfrow = c(2, 2)) 

# plot
autoplot(mod1)
```

##PLU47225 = medium avocado
```{r}
mod2 <- lm(average_price ~ x4225, data = avocado_trim)
summary(mod2)
```


```{r}
par(mfrow = c(2, 2)) 

# plot
autoplot(mod2)
```


##PLU4046 = small avocado
```{r}
mod3 <- lm(average_price ~ x4046, data = avocado_trim)
mod3
```

```{r}
par(mfrow = c(2, 2)) 


autoplot(mod3)
```



```{r}
mod4 <- lm(average_price ~ type, data = avocado_trim)
mod4
```

```{r}
par(mfrow = c(2, 2)) 

# plot
autoplot(mod4)
```




```{r}
mod5 <- lm(average_price ~ year, data = avocado_trim)
mod5
```

```{r}
par(mfrow = c(2, 2)) 

# plot
autoplot(mod5)
```


```{r}
anova(mod1, mod2, mod3, mod4,mod5)
```


```{r}
mod6comb <- lm(average_price ~ type + year, data = avocado_trim)
summary(mod6comb)
```

```{r}
mod7comb <- lm(average_price ~ type + year + x4770, data = avocado_trim)
summary(mod7comb)
```

```{r}
avocado_trim%>%
  ggplot(aes(x = year, y = average_price, colour = type))+
  geom_point()+
  geom_smooth(method = 'lm', se = FALSE)
```

```{r}
avocado_trim%>%
  ggplot(aes(x = year, y = average_price))+
  geom_point()+
  geom_smooth(method = 'lm', se = FALSE)
```



```{r}
avocado_trim%>%
  ggplot(aes(x = average_price, y = type, colour = year))+
  geom_point()+
  geom_smooth(method = 'lm', se = FALSE)
```




##Automated Machine 



```{r}
regsubsets_forwardavocado <-regsubsets(average_price ~.,
                                data= avocado_trim,
                                nvmax = 8,
                                method = 'forward')
```

```{r}
sum_forward <- summary(regsubsets_forwardavocado)
```



```{r}
view(avocado_trim)
```


```{r}
plot(regsubsets_forward,
     scale = 'adjr2')
```

```{r}
plot(regsubsets_forward,
     scale = 'bic')
```



```{r}
plot(sum_forward$rsq,
     type = 'b')
```
#4 variable only anything afer that not significant.


```{r}
plot(sum_forward$bic,
     type = 'b')
```

##Re-run with backward selection now


```{r}
regsubsets_backward <-regsubsets(average_price ~.,
                                data= avocado_trim,
                                nvmax = 8,
                                method = 'backward')
```


```{r}
sum_backward <- summary(regsubsets_backward)
```



```{r}
plot(regsubsets_backward,
     scale = 'adjr2')
```


```{r}
plot(regsubsets_backward,
     scale = 'bic')
```



```{r}
regsubsets_exhaustive <-regsubsets(average_price ~.,
                                data= avocado_trim,
                                nvmax = 8,
                                method = 'exhaustive')
```


```{r}
plot(regsubsets_exhaustive,
     scale = 'adjr2')
```


```{r}
plot(regsubsets_exhaustive,
     scale = 'bic')
```






