---
title: "R Notebook"
output: html_notebook
---
```{r}
library(gtools)
library(tidyverse)


library(readr)
titanic <- read_csv("data/titanic.csv")
View(titanic)
```
```{r}
view(titanic)

```
```{r}

```

```{r}
titanic %>%
  count(class)
```

##should have done full count of class.

```{r}
titanic <- titanic %>%
  mutate(crew = class %in% c("engineering crew", "victualling crew", "restaurant staff", "deck crew"))
```

```{r}
titanic %>%
  count(crew)
```

```{r}
titanic_probs <- titanic %>%
  group_by(crew) %>%
  summarise(prob = sum(survived == "yes") / n()) 

titanic_probs
```
#

```{r}
titanic_probs %>%
  filter(crew == TRUE)
```



```{r}
titanic_crew <-titanic%>%
  filter(fare == 0)
```
###890 crew members - filtered the variable regarding fare.  All who had free passage.
```{r}
crew_survuved <-titanic_crew%>%
  filter(survived == "no")
  
```

##Total of 2207 people on the Titanic
#Total of 890 crew and 1317 passengers
#From the 890 crew 679 did not survive
#From the 890 crew 211 did survive
##Just realised there are some NA in the data set !!


```{r}
crew_survived <-titanic_crew%>%
  filter(survived == "no")%>%
summarise(probabi = n() / nrow(survived))
```

##Not sure why this is not working.


```{r}
view(titanic)

```
```{r}
firstclass <-titanic_passengers <-titanic%>%
  filter(class == ("1st"))
```
```{r}
firstclass%>%
  filter(survived == "no")
```

```{r}
first_not_survived <-firstclass%>%
  filter(survived == "no")%>%
  summarise(prob = sum(firstclass) == "no") / n())
```

###

##324 1st class passengers
##123 did not survive

```{r}
secondclass <-titanic_passengers <-titanic%>%
  filter(class == ("2nd"))
```
##284 2nd class passengers

```{r}
thirdclass <-titanic_passengers <-titanic%>%
  filter(class == ("3rd"))
```
##709 third class passengers.



```{r}
firstclass
```








#Questions - practise the functions learnt during the class
Q1 If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
source("prob.R")

s_one_dice <-rolldie(1)

```


```{r}
roll_less_than_5 <-s_one_dice %>%
  roll_less_than_5 <- s_one_dice%>%
  filter(X1 <5)

prob <- nrow(roll_less_5) / nrow(s_one_dice)
prob
```






##Q2How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
source("prob.R")

s_three_dice <-rolldie(3)
```
##216 obs with 3 variables = 216x3 =648 possible outcomes

##Q3In an experiment where we roll four dice:
##how many outcomes are in the event where the total of the four dice equals 5, 6 or 7)? combination question where the order of the numbers does not matter.
##what is the probability of this event?
##what assumptions do we apply in answering part ii?

```{r}
source("prob.R")

s_four_dice <-rolldie(4)
```

```{r}
number_draws <- s_four_dice%>%
  number_draws <-combinations(5,6,7,1:6)
          

```

```{r}
s_four_dice
```

```{r}
s_four_dice <combinations(5,7,6,6)
```


