---
title: "nhs_cancer"
author: "jane_hogg"
date: "2022-11-28"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```



```{r}
library(tidyverse)
library(janitor)
library(ggplot2)
library(ggpubr)
```

```{r}
library(readr)
cancer_all <- read_csv("data/opendata_inc1620comb_hb (1).csv")
```

```{r}

cancer_all <- clean_names(cancer_all)
```




### Introduction

- The data used is from PHS (Public Health Scotland) and in order to provide an over view of the data I have used the following data set:
2016 - 2021 - Five Year Incidence of Cancer by Health Board


### Purpose of the Data Review

In order to inform current and future planning for provision of cancer treatment services in NHS Borders, you would like to gain a better understanding of the incidence of cancer in NHS Borders.

For example if there is a higher than average type of cancer detected in the Borders, or disparity in the number of cancer patients by gender then resources may need to be allocated in a different way or preventative screening activity increased.


###Overview of Trends in Cancer in NHS Borders
```{r}
cancer_allBorders <-cancer_all %>%
  filter(hb == "S08000016")
```
```{r}
gender_count <-cancer_allBorders%>% 
  select(sex)%>%
  count(sex)
```

```{r}
 cance_gender_incidence <-cancer_allBorders%>% 
  select(sex, incidences_all_ages)%>%
  count(sex, incidences_all_ages)

```


```{r}
cancer_allBorders %>%
  filter(cancer_site == "All cancer types") %>%
  filter(sex != "All") %>%
  ggplot(aes(x = year, y = incidences_all_ages, fill = sex))+
  geom_col(position = "dodge") +
  labs(
    x = "Year",
    title = "All cancer cases in Borders",
    subtitle =  "2016 to 2022",
    y = "Incidence")
```

The data set indicates a slightly higher rate of cancer in men than women in the Borders over the period 2016 - 2022.  


```{r}
  cancer_allBorders%>%
  mutate(sex = "Male")%>%
  ggplot(aes(x = cancer_site, y = incidences_all_ages, fill = "Male"))+
  geom_col(position = "dodge") +
  labs(
    x = "Type of Cancer",
    title = "Male Cancer Types by Age NHS Borders",
    subtitle =  "2016 to 2022",
    y = "Incidence")
```

```{r}
cancer_allBorders%>%
  mutate(sex = "Male")%>%
  ggplot(aes(x = cancer_site, y = incidence_rate_age10to14, fill = "Male"))+
  geom_col(position = "dodge") +
  labs(
    x = "Type of Cancer",
    title = "Male Cancer Types by Age",
    subtitle =  "2016 to 2022",
    y = "Incidence")
```


#Further age profiling of cases is particularly interesting with the highest propensity for cancer coming in the older age profiles would indicate that the highest case are coming from the older age ranges.  In addition that in the Borders there is a growing number of older people - resources may need to be allocated to preventative measures for the older people in the community or increasing take up of screening at key ages (Bowel/Prostrate Screeing)

```{r}
most_common_Cancer <-cancer_allBorders %>%
  filter(cancer_site != "All cancer types") %>%
  filter(sex == "All") %>% 
  filter(year >= 2012) %>%
  group_by(cancer_site) %>%
  summarise(
    cases = sum(incidences_all_ages)
  ) %>%
  top_n(10) %>%
  pull(cancer_site)
```


```{r}
view(most_common_Cancer)
```

1 Basal cell carcinoma of the skin
2 Breast
3 Colon
4 Colorectal cancer
5 Malignant melanoma of the skin
6 Non-Hodgkin lymphoma
7 Non-melanoma skin cancer
8 Rectum and rectosigmoid junction
9 Squamous cell carcinoma of the skin
10 Trachea, bronchus and lung




## Comparing the Border to other local authorities

Borders is geographically spread, rural and with a smaller population in relation to a numbe of other place in Scotland.  Employment is heavily focused on farming.  Comparative analysis across all local authorizes (in particular cities with a higher population) may not be that helpful and so my analysis has focused on a comparable area - Dumfries & Galloway.

```{r}
cancer_dumfries <-cancer_all %>%
  filter(hb == "S08000017")
```

```{r}
cancer_dumfries %>%
  filter(cancer_site == "All cancer types") %>%
  filter(sex != "All") %>%
  ggplot(aes(x = year, y = incidences_all_ages, fill = sex))+
  geom_col(position = "dodge") +
  labs(
    x = "Year",
    title = "All cancer cases in Dumfries",
    subtitle =  "2016 to 2022",
    y = "Incidence")
```
## Interesting that this would suggest that there is little difference between genders in Dumfries.  


```{r}
most_commondumfries <-cancer_dumfries %>%
  filter(cancer_site != "All cancer types") %>%
  filter(sex == "All") %>% 
  filter(year >= 2012) %>%
  group_by(cancer_site) %>%
  summarise(
    cases = sum(incidences_all_ages)
  ) %>%
  top_n(10) %>%
  pull(cancer_site)
```
```{r}
view(most_commondumfries)
```




1 Basal cell carcinoma of the skin
2 Breast
3 Colon
4 Colorectal cancer
5 Head and neck
6 Non-Hodgkin lymphoma
7 Non-melanoma skin cancer
8 Rectum and rectosigmoid junction
9 Squamous cell carcinoma of the skin
10 Trachea, bronchus and lung

There is limited difference in the top 10 types of cancer other than in Dumfries the incidence of Head and Neck related cancer appears in the data.


